Graph-Based Neural Reconstruction from Skeletonized 3D Networks

### 2018-03-02 papers/eccv2018/2_method.tex
paper: added information on augmentations/lifted multicut

\begin{figure}[t]
	\centering
	\includegraphics[width=0.82\linewidth]{./figures/skeleton1.png}
	\includegraphics[width=0.82\linewidth]{./figures/skeleton2.png}
	\includegraphics[width=0.82\linewidth]{./figures/skeleton3.png}
	\caption{Example skeletons (in black) extracted from segments using the TEASER algorithm.}
	\label{fig:skeletonization}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.92\linewidth]{./figures/split_error1.png}
	\includegraphics[width=0.92\linewidth]{./figures/split_error2.png}		\includegraphics[width=0.85\linewidth]{./figures/merge_candidate2.png}
	\caption{Three erroneously split segments.}
	\label{fig:merge_candidates}
\end{figure}

@@

After constructing the 3D graph we apply graph partitioning using multicut to compute the final segmentation. Using top-down graph partitioning allows us to apply biological constraints on the output. Neuroscientists know that neuronal connectivity graphs in the brain are acyclic (i.e., the graphs have a genus of zero). We enforce this constraint by finding a multicut partition of the graph that generates a \textit{forest} of nodes, i.e., a set of trees where no segment has a cycle. To solve this constraing multicut problem we use the method by Keuper et al.~\cite{keuper2015efficient} that produces a feasible solution by greedy additive edge contraction.

>>>>

\begin{figure}[t]
	\centering
	\includegraphics[width=0.32\linewidth]{./figures/skeleton1.png}
	\includegraphics[width=0.32\linewidth]{./figures/skeleton2.png}
	\includegraphics[width=0.32\linewidth]{./figures/skeleton3.png}
	\caption{Example skeletons (in black) extracted from segments using the TEASER algorithm.}
	\label{fig:skeletonization}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=0.32\linewidth]{./figures/split_error1.png}
	\includegraphics[width=0.32\linewidth]{./figures/split_error2.png}		\includegraphics[width=0.32\linewidth]{./figures/merge_candidate2.png}
	\caption{Three erroneously split segments.}
	\label{fig:merge_candidates}
\end{figure}

@@

After constructing the 3D graph we apply graph partitioning using multicut to compute the final segmentation. 
Using top-down graph partitioning allows us to apply biological constraints on the output. 
Formulating the problem as a multicut minimization problem allows us to guarantee \TODO{FIX} globally consistent solutions where every cycle of ``merge" edges is closed \TODO{CONFUSING}.
To solve this constraining multicut problem we use the method by Keuper et al.~\cite{keuper2015efficient} that produces a feasible solution by greedy additive edge contraction.
We extend the multicut formulation the ``lifted" version of the problem where non-adjacent nodes have edge weights corresponding to the probability of belonging to the same neuron \TODO{(CITE)}.
We determine the lifted edge weights following the example of Keuper et al. \cite{keuper2015efficient}.
\TODO{find better source and describe the process}

### 2018-03-02 papers/eccv2018/3_evaluation.tex
brief updates about what to add
paper: added information on augmentations/lifted multicut

The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. A recent study by Funke et al.~\cite{schlegel2017learning} demonstrated superior performance of such methods over existing ones on anisotropic data. We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.

@@

We use the left cylinder of the Kasthuri dataset for training and validation. We train on 80\% of the potential merge candidates for this volume.
We validate the CNN classifier on the remaining 20\% of candidates. We apply data augmentation to the generated examples to increase the size of the training datasets. We consider all rotations of $90$ degrees along the $xy$-plane in addition to mirroring along the $x$ and $z$ axes. This produces 16 times more training data.

We consider networks with varying input sizes, optimizers, loss functions, filter sizes, learning rates, and activation functions. The supplemental material includes information on the experiments that determined these final parameters. Table~\ref{table:architecture} provides the parameters of the final network. There are 7,294,705 learnable parameters in our final architecture. All the parameters are randomly initialized following the Xavier uniform distribution~\cite{glorot2010understanding}. Training concluded after 34 epochs.

@@

>>>>

The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. A recent study by Funke et al.~\cite{funke2017deep} demonstrated superior performance of such methods over existing ones on anisotropic data. We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.

@@

We use half of the Kasthuri dataset for training and validation. 
We train on 80\% of the potential merge candidates for this volume.
We validate the CNN classifier on the remaining 20\% of candidates.

We consider networks with varying input sizes, optimizers, loss functions, filter sizes, learning rates, and activation functions. The supplemental material includes information on the experiments that determined these final parameters. Table~\ref{table:architecture} provides the parameters of the final network. 
There are 7,294,705 learnable parameters in our final architecture. 
All the parameters are randomly initialized following the Xavier uniform distribution~\cite{glorot2010understanding}. 
Training concluded after \TODO{YYY} epochs.

@@

\paragraph{Training Augmentation.}

Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields \TODO{700} positive and \TODO{7000} negative examples.
To avoid overfitting our deep networks, we apply the following augmentations on the example.
During a single batch, we randomly select ten positive examples and ten negative examples. 
With probability 0.5, the example is flipped across the $xy$-plane. 
We then rotate the example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
The supplemental material contains experiments demonstrating that benefits of this augmentation strategy.
We have 20,000 such examples per epoch.

### 2018-03-02 papers/eccv2018/4_results.tex
updated paper to eccv format
paper: added information on augmentations/lifted multicut

Fig.~\ref{fig:positive-results} shows successful merges on the Kasthuri Vol. 2 dataset. Several of these examples combine multiple consecutive segments that span the volume.
In the third example we correct the over-segmentation of a dendrite and attached spine-necks.
Fig.~\ref{fig:negative-results} shows typical failure cases of our method (red circles).
In two of these examples the algorithm correctly predicted several merges before a single error rendered the segment as wrong.
In the third example (blue circle) a merge error in the initial segmentation propagated to our output.
We now analyze how each major component of our method contributes to this final result.

\begin{figure}[t]
	\centering
	\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct1.png}
	\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct2.png}
	\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct3.png}
	\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct4.png}
	\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct5.png}
	\caption{Segments of neurons that were correctly merged by our method.}
	\label{fig:positive-results}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect1.png}
	\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect2.png}
	\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect3.png}
	\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect4.png}
	\caption{Circles indicate areas of wrong merges by our method (red) or by the initial pixel-based segmentation (blue).}
	\label{fig:negative-results}
\end{figure}

@@

@@

>>>>

Fig.~\ref{fig:qualitative-results} shows successful merges on the Kasthuri Vol. 2 dataset. Several of these examples combine multiple consecutive segments that span the volume.
In the third example we correct the over-segmentation of a dendrite and attached spine-necks.
Fig.~\ref{fig:qualitative-results} shows typical failure cases of our method (red circles).
In two of these examples the algorithm correctly predicted several merges before a single error rendered the segment as wrong.
In the third example (blue circle) a merge error in the initial segmentation propagated to our output.
We now analyze how each major component of our method contributes to this final result.

\begin{figure}[t]
	\begin{minipage}{0.45\linewidth}
		\centering
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct1.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct2.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct3.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct4.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-correct5.png}
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\centering
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect1.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect2.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect3.png}
		\includegraphics[width=0.85\linewidth]{./figures/VI-results/multicut-incorrect4.png}
	\end{minipage}
	\caption{(left) Segments of neurons that were correctly merged by our method. (right) Circles indicate areas of wrong merges by our method (red) or by the initial pixel-based segmentation (blue).}
	\label{fig:qualitative-results}
\end{figure}

@@

\paragraph{Inference Augmentation.}

When computing the probability to merge two segments, we input the initial segment into our CNN as well as \TODO{XX} randomly rotated and flipped examples (in the same manner as training augmentation).
This produces some additional increase in overall accuracy (Table ~\ref{table:inference-augmentation}). 
The supplemental material contains experiments showing the trade-offs between increased accuracy and runtime when using these augmentation strategies.

\TODO{Add table for augmentation}

@@

\TODO{How does using lifted-multicut improve the results!}
